Count pages completed in each year

### 2024-06-24 src/count_completed.Rmd
Updated year-end-summary
Updated 04/fda-expert-coi

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(page_update_line==update_text) %>%
    select(-old_link) %>%
    print
  cat("\n\n")
}
```

@@

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(page_update_line==update_text) %>%
    select(-old_link) %>%
    print
  cat("\n\n")
}
```

@@

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(length(old_link) > 0) %>%
    select(yr, old_link) %>%
    print
  cat("\n\n")
}
```

@@

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(length(old_link) == 0) %>%
    select(yr, old_link) %>%
    print
  cat("\n\n")
}
```

>>>>

```{r}
md_files %>%
  filter(page_update_line==update_text) %>%
  select(-old_link)
```

@@

```{r}
md_files %>%
  filter(page_update_line==update_text) %>%
  select(-old_link) %>%
  print
```

@@

```{r}
md_files %>%
  filter(nchar(old_link) > 0) %>%
  glue_data("-   [{fn}]({old_link})\n") -> linked
```

`r paste0(linked, collapse="\n")`

@@

```{r}
md_files %>%
  filter(nchar(old_link) == 0) %>%
  select(yr, fn, old_link)
```
